Jaigo Technical Report

### 2007-12-19 trunk/paper/paper.tex
rotate tables to avoid truncation or splitting

\usepackage{hyperref}
\usepackage{memhfixc}

@@

\begin{titlingpage}
\maketitle

@@

\chapter{Introduction}
%Include background materials and define the problem and scope of your project.
Go is a two-player board game which originated in Ancient China and remains one of the most richly complex games of strategy today. The objective is to control more area or territory than one's opponent on the game board. The game is played on a square line grid; the standard size of this grid is 19 x 19, though 13 x 13 and 9 x 9 grids are used occasionally. Players place stones -- either black or white -- at the intersecting points of the grid to signify control of that position. Once placed on the board a stone has a number of liberties -- unoccupied grid positions which are orthogonally adjacent to that stone. The goal of the game is to claim as much territory as possible by forming chains (contiguous extensions of stones of the same color) which cannot be captured by one's opponent. A stone or chain is captured and removed from the board when it has no liberties, the result of being surrounded by stones of the opposing color.

@@

For the first 50 moves on a 19x19 board with human (black) versus crawler (white),
\begin{tabular}{ccccccccc}
\hline
Function & Calls & Percent & Own Time & Time & Avg & Min & Max & File\\
\hline
(no name) & 109675 & 25.68 & 14310.594ms &	36908.812ms &	0.337ms &	0.059ms	& 1593.542ms	& simple\_go.js (line 407)\\
\hline
flood\_mark & 1618 & 14.17 & 7897.73ms & 25481.245ms & 15.749ms & 0.162ms & 1635.18ms & simple\_go.js (line 807)\\
\hline
(no name) &	194678 &	11.75	& 6551.626ms &	6554.733ms &	0.034ms &	0.008ms &	1555.243ms &	simple\_go.js (line 819)\\
\hline
string\_as\_move &	56065 &	7.48 &	4168.485ms &	4169.549ms &	0.074ms &	0.011ms &	1591.844ms &	simple\_go.js (line 192)\\
\hline
iterate	& 109676 &	7.19 &	4005.749ms &	22595.463ms &	0.206ms &	0.011ms &	1593.499ms &	simple\_go.js (line 391)\\
\hline
(no name) &	283642 &	4.9 &	2732.499ms &	18589.343ms &	0.066ms &	0.015ms &	1593.144ms &	simple\_go.js (line 416)\\
\hline
iterateOwnProperties &	5811	& 4.38	& 2440.378ms &	2847.852ms &	0.49ms &	0.004ms &	2.917ms &	simple\_go.js (line 132)\\
\hline
Set\_Goban &	2150 &	3.53 &	1968.651ms &	1969.095ms &	0.916ms &	0.004ms &	942.058ms &	simple\_go.js (line 528)\\
\hline
(no name) &	42734 &	2.99 &	1666.478ms &	1666.716ms &	0.039ms &	0.008ms &	935.83ms &	simple\_go.js (line 835)\\
\hline
update &	3662 &	2.9 &	1613.61ms &	1614.099ms &	0.441ms &	0.004ms &	1560.416ms &	simple\_go.js (line 117)\\
\hline
Add\_Block &	2340 &	2.8 &	1559.92ms &	1560.774ms &	0.667ms &	0.007ms &	1529.63ms &	simple\_go.js (line 757)\\
\hline
Calculate\_Neighbour &	448	2.67 &	1487.337ms &	12205.939ms &	27.245ms &	0.019ms &	1579.849ms &	simple\_go.js (line 829)\\
\hline
Simple\_Same\_Block &	2149 &	1.93 &	1073.573ms &	8185.472ms &	3.809ms &	0.002ms &	1556.376ms &	simple\_go.js (line 606)\\
\hline
List\_Block\_Liberties &	3210 &	1.56 &	871.609ms &	5057.619ms &	1.576ms &	0.012ms &	1593.058ms &	simple\_go.js (line 863)\\
\hline
\end{tabular}

For the first 100 moves of a game on a 19x19 board, with crawler (black) versus crawler (white),

\begin{tabular}{ccccccccc}
	\hline
	Function & Calls & Percent & Own Time & Time & Avg & Min & Max & File\\	
\hline
(no name) &	404494 &	32.8 &	71255.203ms &	147518.241ms &	0.365ms &	0.059ms &	1650.149ms &	simple\_go.js (line 407)\\
\hline
flood\_mark &	3838 &	15.94 &	34634.022ms &	96713.52ms &	25.199ms &	0.206ms &	1736.537ms &	simple\_go.js (line 807)\\
\hline
iterate &	404495 &	8.75 &	19004.696ms &	76254.33ms &	0.189ms &	0.011ms &	1650.101ms &	simple\_go.js (line 391)\\
\hline
(no name) &	735190 &	8.72 &	18941.197ms &	18941.987ms &	0.026ms &	0.008ms &	1572.648ms &	simple\_go.js (line 819)\\
\hline
string\_as\_move &	242765 &	5.86 &	12724.373ms	& 12725.279ms &	0.052ms &	0.011ms &	1629.186ms &	simple\_go.js (line 192)\\
\hline
(no name) &	1041519 &	4.7 &	10209.513ms &	57248.372ms &	0.055ms &	0.015ms &	1649.869ms &	simple\_go.js (line 416)\\
\hline
List\_Block\_Liberties &	7706 &	4.02 &	8727.331ms &	21457.809ms &	2.785ms &	0.013ms &	1630.607ms &	simple\_go.js (line 863)\\
\hline
iterateOwnProperties &	14752 &	3.68 &	7985.019ms &	9340.503ms &	0.633ms &	0.004ms &	2.419ms &	simple\_go.js (line 132)\\
\hline
update &	8742 &	3.18 &	6911.102ms &	6911.93ms &	0.791ms &	0.004ms &	1648.007ms &	simple\_go.js (line 117)\\
\hline
Calculate\_Neighbour &	661 &	3.03 &	6593.032ms &	60385.478ms &	91.355ms &	0.115ms &	1679.244ms &	simple\_go.js (line 829)\\
\hline
(no name) &	160414 &	2.51 &	5444.827ms &	5445.809ms &	0.034ms	& 0.008ms &	944.464ms &	simple\_go.js (line 835)\\
\hline
Add\_Stone &	6010 &	1.1 &	2392.214ms	& 191461.602ms	& 31.857ms &	1.524ms &	1785.447ms &	simple\_go.js (line 641)\\
\hline
\end{tabular}

@@

%(7)    References.

\bibliography{paper}
\bibliographystyle{plain}
\end{document}

>>>>

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{memhfixc}

@@

\frontmatter
\begin{titlingpage}
\maketitle

@@

\mainmatter
\chapter{Introduction}
%Include background materials and define the problem and scope of your project.
Go is a two-player board game which originated in Ancient China and remains one of the most richly complex games of strategy today. The objective is to control more area or territory than one's opponent on the game board. The game is played on a square line grid; the standard size of this grid is 19 x 19, though 13 x 13 and 9 x 9 grids are used occasionally. Players place stones -- either black or white -- at the intersecting points of the grid to signify control of that position. Once placed on the board a stone has a number of liberties -- unoccupied grid positions which are orthogonally adjacent to that stone. The goal of the game is to claim as much territory as possible by forming chains (contiguous extensions of stones of the same color) which cannot be captured by one's opponent. A stone or chain is captured and removed from the board when it has no liberties, the result of being surrounded by stones of the opposing color.

@@

\tref{table:first50} shows the first 50 moves on a 19x19 board with human (black) versus crawler (white).
\begin{table}
  \rotatebox{90}{
    \begin{tabular}{ccccccccc} \toprule
      Function & Calls & Percent & Own Time (ms) & Time (ms) & Avg (ms) & Min (ms) & Max (ms) & File\\ \midrule
      (no name) & 109675 & 25.68 & 14310.594 &	36908.812 &	0.337 &	0.059	& 1593.542	& simple\_go.js (line 407)\\
      flood\_mark & 1618 & 14.17 & 7897.73 & 25481.245 & 15.749 & 0.162 & 1635.18 & simple\_go.js (line 807)\\
      (no name) &	194678 &	11.75	& 6551.626 &	6554.733 &	0.034 &	0.008 &	1555.243 &	simple\_go.js (line 819)\\
      string\_as\_move &	56065 &	7.48 &	4168.485 &	4169.549 &	0.074 &	0.011 &	1591.844 &	simple\_go.js (line 192)\\
      iterate	& 109676 &	7.19 &	4005.749 &	22595.463 &	0.206 &	0.011 &	1593.499 &	simple\_go.js (line 391)\\
      (no name) &	283642 &	4.9 &	2732.499 &	18589.343 &	0.066 &	0.015 &	1593.144 &	simple\_go.js (line 416)\\
      iterateOwnProperties &	5811	& 4.38	& 2440.378 &	2847.852 &	0.49 &	0.004 &	2.917 &	simple\_go.js (line 132)\\
      Set\_Goban &	2150 &	3.53 &	1968.651 &	1969.095 &	0.916 &	0.004 &	942.058 &	simple\_go.js (line 528)\\
      (no name) &	42734 &	2.99 &	1666.478 &	1666.716 &	0.039 &	0.008 &	935.83 &	simple\_go.js (line 835)\\
      update &	3662 &	2.9 &	1613.61 &	1614.099 &	0.441 &	0.004 &	1560.416 &	simple\_go.js (line 117)\\
      Add\_Block &	2340 &	2.8 &	1559.92 &	1560.774 &	0.667 &	0.007 &	1529.63 &	simple\_go.js (line 757)\\
      Calculate\_Neighbour &	448 &	2.67 &	1487.337 &	12205.939 &	27.245 &	0.019 &	1579.849 &	simple\_go.js (line 829)\\
      Simple\_Same\_Block &	2149 &	1.93 &	1073.573 &	8185.472 &	3.809 &	0.002 &	1556.376 &	simple\_go.js (line 606)\\
      List\_Block\_Liberties &	3210 &	1.56 &	871.609 &	5057.619 &	1.576 &	0.012 &	1593.058 &	simple\_go.js (line 863)\\ \bottomrule
  \end{tabular}}
  \caption{First 50 moves on a 19x19 board}
  \label{table:first50}
\end{table}

\tref{table:first100} shows the first 100 moves of a game on a 19x19 board, with crawler (black) versus crawler (white).

\begin{table}
  \rotatebox{90}{
    \begin{tabular}{ccccccccc} \toprule
      Function & Calls & Percent & Own Time & Time & Avg & Min & Max & File\\	\midrule
      (no name) &	404494 &	32.8 &	71255.203 &	147518.241 &	0.365 &	0.059 &	1650.149 &	simple\_go.js (line 407)\\
      flood\_mark &	3838 &	15.94 &	34634.022 &	96713.52 &	25.199 &	0.206 &	1736.537 &	simple\_go.js (line 807)\\
      iterate &	404495 &	8.75 &	19004.696 &	76254.33 &	0.189 &	0.011 &	1650.101 &	simple\_go.js (line 391)\\
      (no name) &	735190 &	8.72 &	18941.197 &	18941.987 &	0.026 &	0.008 &	1572.648 &	simple\_go.js (line 819)\\
      string\_as\_move &	242765 &	5.86 &	12724.373	& 12725.279 &	0.052 &	0.011 &	1629.186 &	simple\_go.js (line 192)\\
      (no name) &	1041519 &	4.7 &	10209.513 &	57248.372 &	0.055 &	0.015 &	1649.869 &	simple\_go.js (line 416)\\
      List\_Block\_Liberties &	7706 &	4.02 &	8727.331 &	21457.809 &	2.785 &	0.013 &	1630.607 &	simple\_go.js (line 863)\\
      iterateOwnProperties &	14752 &	3.68 &	7985.019 &	9340.503 &	0.633 &	0.004 &	2.419 &	simple\_go.js (line 132)\\
      update &	8742 &	3.18 &	6911.102 &	6911.93 &	0.791 &	0.004 &	1648.007 &	simple\_go.js (line 117)\\
      Calculate\_Neighbour &	661 &	3.03 &	6593.032 &	60385.478 &	91.355 &	0.115 &	1679.244 &	simple\_go.js (line 829)\\
      (no name) &	160414 &	2.51 &	5444.827 &	5445.809 &	0.034	& 0.008 &	944.464 &	simple\_go.js (line 835)\\
      Add\_Stone &	6010 &	1.1 &	2392.214	& 191461.602	& 31.857 &	1.524 &	1785.447 &	simple\_go.js (line 641)\\ \bottomrule
    \end{tabular}}
  \caption{First 100 moves on a 19x19 board}
  \label{table:first100}
\end{table}

@@

\backmatter
\bibliography{paper}
\bibliographystyle{plain}
\end{document}
